---
title: "Chipotle HW in R"
output: html_notebook
---

In this assignment, we'll redo the chipotle exercises from HW 3 in R. We'll do this using packages from the TidyVerse.

```{r}
# Q. 1
library(tidyverse)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

```{r}
# Q.2
url = 'https://raw.githubusercontent.com/TheUpshot/chipotle/master/orders.tsv'
chipo = read_tsv(url)
```

```{r}
# Q. 3
chipo %>% head(n=10)
chipo %>% tail(n=10)
```
```{r}
# Q. 4
chipo %>% summary()
```


```{r}
# Q. 5
chipo %>% nrow()
```
```{r}
# Q. 6
chipo %>% ncol()
```

```{r}
# Q. 7
chipo %>% colnames()
```

```{r}
# Q. 8
# The index is not shown.
```


```{r}
# Q. 9
chipo %>% select(quantity) %>%  sum()
```

```{r}
# Q. 10
chipo %>% 
  group_by(item_name) %>% 
  summarise(sum(quantity)) %>% 
  arrange(desc(`sum(quantity)`)) %>% 
  head()
```
```{r}
# Q.11
chipo %>% 
  group_by(choice_description) %>% 
  summarise(sum(quantity)) %>% 
  arrange(desc(`sum(quantity)`)) %>% 
  head()
```
```{r}
# Q.12
chipo$item_price = gsub('[$,]', '', chipo$item_price) %>% as.numeric()
```

```{r}
# Q.13
chipo %>% 
  select(order_id) %>% 
  unique() %>% 
  nrow()

# length(unique(chipo$order_id))
```
```{r}
chipo %>% filter(item_name == '6 Pack Soft Drink') %>%  head()
```

```{r}
# Q. 15
chipo$item_price %>% sum()
```
```{r}
# Q. 16
chipo %>% group_by(order_id) %>% 
  summarise(ordersum=sum(item_price)) %>% 
  summarise(mean(ordersum))
```
```{r}
# Q. 17
length(unique(chipo$item_name))
```
```{r}
# Q. 18
chipo %>% filter(item_price > 10.00) %>% nrow()
```

```{r}
# Q. 19
chipo %>% filter(item_name == 'Barbacoa Bowl') %>%  head()
```

```{r}
# Q. 20

# Attempt 1
# ave_price = function(x) {
#   total_quantity = sum(x$quantity)
#   total_revenue = sum(x$item_price)
#   total_revenue/total_quantity
# }
# chipo %>% 
#   group_by(item_name) %>% 
#   do(ave_price=round(sum(.$quantity)/sum(.$item_price), digits=2)) %>% 
#   arrange(desc(ave_price))

# Attempt 2
df = chipo %>% 
  group_by(item_name) %>% 
  summarise(total_quantity=sum(quantity), total_revenue=sum(item_price))
df = df %>% 
  mutate(ave_price=round(total_revenue/total_quantity, digits=2)) %>% 
  select(item_name, ave_price) %>%
  arrange(ave_price)
df %>% head()
```
```{r}
# Q. 21
df %>% 
  arrange(item_name) %>% 
  head()
```
```{r}
# Q. 22
# Inefficient method
chipo %>% arrange(desc(item_price)) %>% head(1)
# More efficient
chipo[which.max(chipo$item_price),]
```

```{r}
# Q. 23
chipo %>% filter(item_name == 'Veggie Salad Bowl') %>% nrow()
```
```{r}
# Q. 24 
chipo %>% filter(item_name == 'Bottled Water', quantity > 1) %>% nrow()
```
```{r}
# Q. 25
c = chipo %>% 
  group_by(item_name) %>% 
  summarise(total_orders=sum(quantity)) %>% 
  arrange(desc(total_orders)) %>% 
  head(5)
ggplot(c) + aes(x=item_name, y =total_orders) + geom_bar(stat = "identity")
```

